Shallow EDSLs and Object-Oriented Programming

### 2019-01-30 Programming19/Main.tex
Add author info and fix margin problems

\author[a]{Weixin Zhang}
\authorinfo[weixin]{is a PhD student at the University of Hong Kong. Contact him at wxzhang2@cs.hku.hk}
\author[a]{Bruno C. d. S. Oliveira}
\affiliation[a]{The University of Hong Kong, Hong Kong, China}

@@

\textbf{Grounding.}
We make our arguments by using Gibbons and Wu's examples, where procedural
abstraction is used in Haskell to model a simple shallow EDSL. We recode that
EDSL in Scala and with an improved OO-inspired Haskell encoding.
We further illustrate our approach with
a case study on refactoring a deep external SQL DSL implementation to make it
more modular, shallow, and embedded.

>>>>

\author[a]{Weixin Zhang}
\authorinfo[weixin]{is a PhD candidate at the University of Hong Kong. His
  current research interests are centered around modularity, domain-specific languages
  and generative programming. You can contact him at \email{wxzhang2@cs.hku.hk}
  and find further information at \url{https://wxzh.github.io}.
}
\author[a]{Bruno C. d. S. Oliveira}
\authorinfo[bruno]{is an assistant professor of the at the University of Hong Kong. His
  research interests are centered around programming languages. His existing
  research is mainly focused on type systems for modularity and the combination
  of Object-Oriented and Functional Paradigms. You can contact him at
  \email{bruno@cs.hku.hk} and find further information at \url{https://i.cs.hku.hk/~bruno}.}
\affiliation[a]{The University of Hong Kong, Hong Kong, China}

@@

\textbf{Grounding.}
We make our arguments by using Gibbons and Wu's examples, where procedural
abstraction is used in Haskell to model a simple shallow EDSL. We recode that
EDSL in Scala and with an improved OO-inspired Haskell encoding.
We further illustrate our approach with
a case study on refactoring a deep external SQL query processor to make it
more modular, shallow, and embedded.
